Interactive Markdown to explore Clustering

### 2017-02-03 src/ClusterComparison.Rmd
as viewed with WTK and SP

#Visualize Dendrograms
clustering <- reactive({
    dynamicCluster(t(m.sub), dm=input$dm,
				 lk=input$lk,
				 ds=as.numeric(input$ds),
				 output="Cluster")
})

@@

>>>>

#Visualize Dendrograms
clustering <- reactive({
    dynamicCluster(t(m.sub), dm=input$dm,
				 lk=input$lk,
				 ds=as.numeric(input$ds),
				 output="Cluster",
				 minSize=15)
})

@@

    genes <- c("Acta2","Csn3","Epcam","Krt8")
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=1000, height=1000)
